Estimating duration in the presence of misclassification

### 2024-02-05 cis-imperfect-testing.tex

This could be incorporated into the simulation study be generating test results at ...
Adapting the simulation study to incorporate this test sensitivity is much more similar to the data (see purple histogram in \cref{imperf-test:fig:sim-single-pos}).
This model does not require low test sensitivities early in the infection, maintaining compatibility with the results in \cref{E-ATACCC}.

>>>>

This could be incorporated into the simulation study be generating test results at ...\todo{finish sentence}
Adapting the simulation study to incorporate this test sensitivity is much more similar to the data (see purple histogram in \cref{imperf-test:fig:sim-single-pos}).
This model does not require low test sensitivities early in the infection, maintaining compatibility with the results in \cref{E-ATACCC}.
